---
title: "Barriers to data sharing in music psychology"
author: "Tuomas Eerola"
format: html
---

This repository contains the survey data concerning barriers to data sharing in music psychology. The survey replicates the work by Houtkoop, Chambers, Macleod, Bishop, Nichols, and Wagenmaker ([2018](https://doi.org/10.1177/2515245917751886)), who surveyed why scholars (psychologists) may not want to share the data.

Last run: _29/9/2025_

```{r}
#| id: load-libraries
#| echo: false
#| warning: false
#| message: false

source('scr/libraries.R')
source('scr/read_custom_qualtrics.R')
options(scipen=999)

```

## Read data

```{r}
#| id: data
#| echo: true
fn <- "data/Barriers29092025.csv"
Data <- read_custom_qualtrics(filename = fn, format = "labels")
source('scr/rename_variables.R')
```

### Descriptives

```{r}
#| id: describe
#| echo: true
#| warning: false
#| message: false
#| fig.height: 7
#| fig.width: 9
#| output: asis

source('scr/describe_data.R')
print(fig_careerstage)
print(fig_shared)

```

### Main barriers

```{r}
#| id: figures-main
#| echo: true
#| fig.height: 9
#| fig.width: 12
#| warning: false
#| message: false

source('scr/figure_main.R')

```

### Desirability of sharing?

```{r}
#| id: figures-main2
#| echo: true
#| fig.height: 5
#| fig.width: 12
#| eval: true

print(g2)
print(g3)

```

### Share in future and benefits of sharing?

```{r}
#| id: figures-supporting
#| echo: true
#| fig.height: 4.5
#| fig.width: 12

source('scr/figure_supporting.R')

```

